### 2017-10-11 manuscript.rmd
parses bootstrap and psoterior trees

	# Configure knitr, see http://yihui.name/knitr/options
	opts_knit$set( progress = TRUE, verbose = TRUE )

@@

	# Set paths to input data
	input_file_ml = "agalma/Outfiles/RAxML_bipartitions.alignment.fa"

@@

```{r load_data, include=FALSE, cache=TRUE}

	species_tree = ape::read.tree( input_file_ml )

@@

  #medusozoa_node = getMRCA( species_tree, c("Alatina_alata", "Nanomia_bijuga") )

  #species_tree = phytools::reroot( species_tree, medusozoa_node )

>>>>

	# Configure knitr, see http://yihui.name/knitr/options
	opts_knit$set( 
	  progress = TRUE, 
	  verbose = TRUE, 
	  include=FALSE, 
	  cache=TRUE
	 )

@@

	# Set paths to input data
	tree_path = "agalma/Outfiles/"
	input_file_ml = paste( tree_path, "RAxML_bipartitions.alignment.fa", sep="" )
	input_file_bootstraps = paste( tree_path, "RAxML_bootstrap.alignment.fa", sep="" )

	input_files_phylobayes = list.files( 
	  path=tree_path, 
	  pattern="chain\\d+_trimmed60_poisson.treelist" 
	 )

	# Analysis parameters
	burn_in = 400

@@

```{r load_data}

	species_tree = ape::read.tree( input_file_ml )
  bootstrap_trees = ape::read.tree( input_file_bootstraps )

  phylobayes_trees = sapply(
    input_files_phylobayes,
    function( pb ) {
      ape::read.tree( 
        paste( tree_path, pb, sep = "" ) 
      )[ -(1:burn_in)  ]
    }
  )

  phylobayes_trees = unlist( phylobayes_tree,recursive=FALSE )

@@
